---
title: "Difficulty"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{difficulty}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library("marbleCircuit")
library("tidyverse"); theme_set(theme_bw())
```

```{r summarize}
d <- data.frame(Challenge = 1:64) %>%
  group_by(Challenge) %>%
  mutate(
    Missing = sum(missing(Challenge)),
    Difficulty = permutations(missing(Challenge)))
```

A simplistic way to consider difficulty is simply the number of tiles that
are missing. 
Based on the graph below it looks like this is exactly how the challenges
are numbered. 

```{r missing}
ggplot(d, aes(Challenge, Missing)) + 
  geom_point() + 
  scale_y_log10() +
  labs(title = "Number of Missing Tiles")
```

A more sophisticated approach to difficulty recognizes that if there are
repeated tiles that are missing, 
then the difficulty is not as high as when there are more distinct
tiles. 
The graph below plots this notion of difficulty. 

```{r difficulty}
ggplot(d, aes(Challenge, Difficulty)) + 
  geom_point() + 
  scale_y_log10() +
  labs(title = "Difficulty of Challenges")
```

The y-axis in this graph is on a logarithmic axis.
Thus the same distance on the y-axis should be understood as a multiplicative change in the difficulty. 
So moving from 10 to 100 to 1,000 to 10,000 which is the same distance on the 
y-axis is clearly a 10-fold change in difficulty every time. 

Notice that the difficulty is no longer monotonic as there are times
when higher numbered challenges have lower difficulty. 
